Approximation as Differentiation: Notes

### 2025-05-16 main/formal-structures.tex
LatGal has biproducts.

An further important property is that the projections $\pi_1: X \times Y \to X$ and $\pi_2: X \times Y \to Y$,
where $X \times Y$ denotes the product of lattices, have both and upper adjoints. This means $X \times Y$ is
both a product and a coproduct in $\LatGal$, which we write as $X \biprod Y$, with projections $\biproj_X$ and
$\biproj_Y$ and injections $\biinj_X$ and $\biinj_Y$.

@@

\noindent The trivial 1-point lattice is the unit for $\biprod$ and is both terminal and initial. Although the
presence of biproducts is incompatible with $\LatGal$ itself being Cartesian closed, the biproduct structure
will prove crucial for a establishing a Cartesian closed setting for interpreting higher-order programs.

>>>>

Another notable property of $\LatGal$ is that the projections $\pi_1: X \times Y \to X$ and $\pi_2: X \times Y
\to Y$, where $X \times Y$ denotes the product of lattices, have both upper and lower adjoints. This means $X
\times Y$, which we shall hereafter write as $X \biprod Y$, acts as both a product and a coproduct, with
projections $\biproj_X$ and $\biproj_Y$ and injections $\biinj_X$ and $\biinj_Y$.

@@

\noindent The trivial 1-point lattice, which is both terminal and initial, is the unit for $\biprod$. Although
the presence of biproducts is incompatible with $\LatGal$ itself being Cartesian closed, the biproduct
structure will prove crucial for a establishing a Cartesian closed setting for interpreting higher-order
programs for Galois slicing.
